---
title: Hookworm parasitism shapes energy status and cardiovascular disease risk in northeast Madagascar
author: "Lev Kolinski"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: TRUE 
    toc_float: TRUE
    toc_depth: 4
---

# Setup & Data Wrangling

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(MuMIn)
library(tidySEM)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
library(ggplotify)
library(magick)
library(gt)
library(lavaan)
library(kableExtra)
library(boot)
library(car)
library(patchwork)

# ─────────────────────────────────────────────────────────────────────────────
# Plotting function: model-averaged coefficient plot (shared axes version)
# ─────────────────────────────────────────────────────────────────────────────
plot_modelavg_coef_shared <- function(coef_table, plot_title,
                                      x_limits = NULL,
                                      size_limits = c(1.5, 4),
                                      importance_limits) {
  ggplot(coef_table, aes(x = Estimate, y = PrettyVar)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray60") +
    # 90% CI (thick)
    geom_segment(
      aes(x = CI_lower_90, xend = CI_upper_90, y = PrettyVar, yend = PrettyVar),
      linewidth = 1
    ) +
    # 95% CI (thin)
    geom_segment(
      aes(x = CI_lower_95, xend = CI_upper_95, y = PrettyVar, yend = PrettyVar),
      linewidth = 0.5
    ) +
    geom_point(aes(size = Importance), color = "black") +
    scale_size_continuous(
      limits = importance_limits,
      range  = size_limits,
      breaks = c(0.1, 0.3, 0.6, 1.0),
      labels = c("0.1", "0.3", "0.6", "1.0"),
      name   = "Variable importance\n(Akaike weight)"
    ) +
    coord_cartesian(xlim = x_limits) +
    labs(x = "", y = "", title = plot_title) +
    theme_minimal() +
    theme(
      axis.text.y  = element_text(size = 14),
      axis.text.x  = element_text(size = 14),
      plot.title   = element_text(size = 18, face = "bold")
    )
}

# ─────────────────────────────────────────────────────────────────────────────
# Helper: extract coefficient table from a model.avg object
# ─────────────────────────────────────────────────────────────────────────────
var_labels <- c(
  "age"                              = "Age",
  "I(age^2)"                         = "Age\u00B2",
  "age2"                             = "Age\u00B2",
  "BMI"                              = "BMI",
  "log_BMI"                          = "BMI",
  "bin_pos_necator"                  = "N. americanus",
  "bin_pos_ancylostoma"              = "A. ceylanicum",
  "gender_f"                         = "Female",
  "wealth_index"                     = "Wealth",
  "villageMandena"                   = "Village M",
  "villageSarahandrano"              = "Village S",
  "bin_pos_necator:wealth_index"     = "N. americanus*Wealth",
  "bin_pos_ancylostoma:wealth_index" = "A. ceylanicum*Wealth",
  "bin_pos_necator:gender_f"         = "N. americanus*Female",
  "bin_pos_ancylostoma:gender_f"     = "A. ceylanicum*Female"
)

master_var_order <- c(
  "Age", "Age\u00B2", "Female", "Village M", "Village S",
  "BMI", "Wealth",
  "N. americanus*Wealth", "A. ceylanicum*Wealth",
  "N. americanus", "A. ceylanicum"
)

master_var_order_bmi <- c(
  "Age", "Age\u00B2", "Female", "Village M", "Village S",
  "Wealth",
  "N. americanus*Wealth", "A. ceylanicum*Wealth",
  "N. americanus", "A. ceylanicum"
)

master_var_order_sex <- c(
  "Age", "Age\u00B2", "Female", "Village M", "Village S",
  "BMI", "Wealth",
  "N. americanus*Female", "A. ceylanicum*Female",
  "N. americanus*Wealth",     "A. ceylanicum*Wealth",
  "N. americanus", "A. ceylanicum"
)

master_var_order_bmi_sex <- c(
  "Age", "Age\u00B2", "Female", "Village M", "Village S",
  "Wealth",
  "N. americanus*Female", "A. ceylanicum*Female",
  "N. americanus*Wealth",     "A. ceylanicum*Wealth",
  "N. americanus", "A. ceylanicum"
)

extract_coef_table <- function(model_avg_obj, labels = NULL) {
  df <- summary(model_avg_obj)$coefmat.full %>%
    as.data.frame() %>%
    tibble::rownames_to_column(var = "Variable") %>%
    filter(Variable != "(Intercept)") %>%
    mutate(
      CI_lower_95 = Estimate - 1.96  * `Std. Error`,
      CI_upper_95 = Estimate + 1.96  * `Std. Error`,
      CI_lower_90 = Estimate - 1.645 * `Std. Error`,
      CI_upper_90 = Estimate + 1.645 * `Std. Error`
    )

  imp <- sw(model_avg_obj)

  df <- df %>%
    rowwise() %>%
    mutate(
      Importance = {
        if (Variable %in% names(imp)) {
          imp[Variable]
        } else {
          matched_var <- names(imp)[sapply(names(imp), function(v) startsWith(Variable, v))]
          if (length(matched_var) > 0) imp[matched_var[1]] else NA
        }
      }
    ) %>%
    ungroup() %>%
    mutate(PrettyVar = dplyr::recode(Variable, !!!labels))

  df$PrettyVar[is.na(df$PrettyVar)] <- df$Variable
  df
}

complete_coef_table <- function(df, full_order) {
  template <- tibble(PrettyVar = full_order)
  df2 <- template %>% left_join(df, by = "PrettyVar")
  df2$PrettyVar <- factor(df2$PrettyVar, levels = full_order)
  df2
}

# ─────────────────────────────────────────────────────────────────────────────
# Helper: stack multiple coef tables with an Outcome label
# ─────────────────────────────────────────────────────────────────────────────
bind_coef_tables <- function(..., outcomes) {
  tables <- list(...)
  purrr::map2_dfr(tables, outcomes, ~ mutate(.x, Outcome = .y))
}

# ─────────────────────────────────────────────────────────────────────────────
# Plotting function: overlaid estimates, colored by outcome (for blood pressure)
# ─────────────────────────────────────────────────────────────────────────────
plot_combined_outcomes <- function(combined_df, plot_title,
                                   x_limits = NULL,
                                   size_limits = c(1.5, 4),
                                   importance_limits,
                                   outcome_colors) {
  
  # Dodge offset so CIs don't overlap
  dodge_amt <- 0.35
  
  combined_df <- combined_df %>%
    mutate(Outcome = factor(Outcome, levels = names(outcome_colors)))
  
  # Numeric y position for dodging (ggplot handles factor y poorly with segments)
  n_outcomes <- length(unique(combined_df$Outcome))
  outcome_levels <- levels(combined_df$Outcome)
  
  combined_df <- combined_df %>%
    mutate(
      y_num    = as.numeric(PrettyVar),
      out_idx  = as.numeric(Outcome),
      y_dodge  = y_num - (out_idx - (n_outcomes + 1) / 2) * dodge_amt
    )
  
  var_levels <- levels(combined_df$PrettyVar)
  
  ggplot(combined_df) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray60") +
    
    # 95% CI (thin)
    geom_segment(
      aes(x = CI_lower_95, xend = CI_upper_95,
          y = y_dodge, yend = y_dodge,
          color = Outcome),
      linewidth = 0.5
    ) +
    
    # 90% CI (thick)
    geom_segment(
      aes(x = CI_lower_90, xend = CI_upper_90,
          y = y_dodge, yend = y_dodge,
          color = Outcome),
      linewidth = 1.5
    ) +
    
    # Point estimate
    geom_point(
      aes(x = Estimate, y = y_dodge,
          color = Outcome, size = Importance)
    ) +
    
    scale_color_manual(values = outcome_colors, name = "Outcome") +
    
    scale_size_continuous(
      limits = importance_limits,
      range  = size_limits,
      breaks = c(0.1, 0.3, 0.6, 1.0),
      labels = c("0.1", "0.3", "0.6", "1.0"),
      name   = "Variable importance\n(Akaike weight)"
    ) +
    
    scale_y_continuous(
      breaks = seq_along(var_levels),
      labels = var_levels,
      expand = expansion(mult = 0.05)
    ) +
    
    coord_cartesian(xlim = x_limits) +
    labs(x = NULL, y = "", title = plot_title) +
    theme_minimal() +
    theme(
      axis.text.y = element_text(size = 13),
      axis.text.x = element_text(size = 13),
      plot.title  = element_text(size = 16, face = "bold"),
      legend.title = element_text(size = 12),
      legend.text  = element_text(size = 11)
    )
}

# ─────────────────────────────────────────────────────────────────────────────
# Helper: mean (SD) string
# ─────────────────────────────────────────────────────────────────────────────
mean_sd <- function(x) {
  sprintf("%.1f (%.1f)", mean(x, na.rm = TRUE), sd(x, na.rm = TRUE))
}
```

## Load & merge data

```{r load-data}
demo_data <- read.csv("/Users/levkolinski/Library/CloudStorage/Box-Box/EEID_Data_public/clean_data_tables/NIH Human Surveys/Survey_Demographic_Health.csv") |>
  mutate(across(starts_with(c("own_", "banking")), ~ifelse(. == "Yes", 1L, 0L)))

infection_data <- read.csv("/Users/levkolinski/Library/CloudStorage/Box-Box/EEID_Data_public/clean_data_tables/HUMAN_PARASITE_ALL_VILLAGE.csv")

infection_data$social_netid <- gsub("\\.", "", infection_data$social_netid)
demo_data$social_netid      <- gsub("\\.", "", demo_data$social_netid)

merged_df <- inner_join(demo_data, infection_data, by = "social_netid") |>
  filter(social_netid != "ESNH248") |>
  mutate(
    pos_necator     = ifelse((NC_reads > 500) & (Necator_americanus > 0.01),    1, 0),
    pos_ancylostoma = ifelse((NC_reads > 500) & (Ancylostoma_ceylanicum > 0.01), 1, 0)
  )
```

## Feature engineering

```{r feature-engineering}
merged_df <- merged_df |>
  mutate(across(contains("systolic"),  as.numeric),
         across(contains("diastolic"), as.numeric),
         across(contains("height"),    as.numeric),
         across(contains("weight"),    as.numeric),
         age = as.numeric(age),
         average_systolic  = (systolic1  + systolic2  + systolic3)  / 3,
         average_diastolic = (diastolic1 + diastolic2 + diastolic3) / 3,
         BMI = weight / height^2,
         material_floor = ifelse(
           grepl("bamboo|rafia|ravenala|dirt", material_floor), 0L,
           ifelse(material_floor == "wood_planks", 1L,
                  ifelse(material_floor == "cement", 2L, material_floor))
         ) |> as.integer(),
         house_toilet = ifelse(
           grepl("In the river|No facility/bush/field", house_toilet), 0L,
           ifelse(house_toilet == "Pit latrine", 1L,
                  ifelse(house_toilet == "Improved pit latrine (Kabone)", 2L, house_toilet))
         ) |> as.integer(),
         material_wall = ifelse(
           grepl("bamboo|rafia|ravenala|mud|compacted_earth", material_wall), 0L,
           ifelse(material_wall == "wood_planks", 1L,
                  ifelse(grepl("brick_fired|brick_unfired", material_wall), 2L,
                         ifelse(material_wall == "metal_sheets", 3L,
                                ifelse(material_wall == "cement", 4L, material_wall))))
         ) |> as.integer(),
         material_roof = ifelse(
           grepl("thatch|bamboo", material_roof), 0L,
           ifelse(material_roof == "metal_sheets", 1L,
                  ifelse(material_roof == "cement", 2L, material_roof))
         ) |> as.integer()
  ) |>
  rowwise() |>
  mutate(
    cgsol = sum(own_cellphone + own_generator + own_tv + own_bicycle +
                  own_motorcycle + own_refrigerator + own_computer, na.rm = TRUE),
    village = ifelse(village.x == "Ampandrana", "Andatsakala", village.x)
  ) |>
  ungroup() |>
  mutate(hsol = material_wall + material_roof + material_floor)

# Select & derive model variables
merged_df_for_model <- merged_df |>
  select(average_systolic, average_diastolic, BMI, age, gender, village,
         cgsol, hsol, contains("pos"), Necator_americanus, Ancylostoma_ceylanicum) |>
  mutate(
    bin_pos_necator       = as.integer(pos_necator),
    bin_pos_ancylostoma   = as.integer(pos_ancylostoma),
    bin_systolic_htn      = ifelse(average_systolic  >= 130, 1L, 0L),
    bin_diastolic_htn     = ifelse(average_diastolic >= 80,  1L, 0L),
    bin_systolic_htn_who  = ifelse(average_systolic  >= 140, 1L, 0L),
    bin_diastolic_htn_who = ifelse(average_diastolic >= 90,  1L, 0L)
  ) |>
  drop_na()

merged_df_for_model$gender_f <- NA
merged_df_for_model$gender_f[merged_df_for_model$gender == "Female"] <- 1L
merged_df_for_model$gender_f[merged_df_for_model$gender == "Male"]   <- 0L

# Infection group labels (for descriptive stats)
merged_df_for_descriptive_stats <- merged_df_for_model %>%
  mutate(
    infection_status = case_when(
      bin_pos_necator == 0 & bin_pos_ancylostoma == 0 ~ "Uninfected",
      bin_pos_necator == 1 & bin_pos_ancylostoma == 0 ~ "Necator infected",
      bin_pos_necator == 0 & bin_pos_ancylostoma == 1 ~ "Ancylostoma infected",
      bin_pos_necator == 1 & bin_pos_ancylostoma == 1 ~ "Co-infected"
    ),
    village = case_when(
      village == "Sarahandrano" ~ "Village S",
      village == "Mandena"      ~ "Village M",
      village == "Andatsakala"  ~ "Village A"
    )
  )

# Scale continuous predictors
merged_df_for_model$age_raw  <- merged_df_for_model$age
merged_df_for_model$age      <- scale(merged_df_for_model$age)
merged_df_for_model$log_BMI  <- scale(log(as.numeric(merged_df_for_model$BMI)))
merged_df_for_model$cgsol    <- scale(merged_df_for_model$cgsol)
merged_df_for_model$hsol     <- scale(merged_df_for_model$hsol)
merged_df_for_model$log_diastolic <- scale(log(as.numeric(merged_df_for_model$average_diastolic)))
merged_df_for_model$log_systolic  <- scale(log(as.numeric(merged_df_for_model$average_systolic)))

# Wealth index (PCA of hsol + cgsol)
pca_wealth <- prcomp(merged_df_for_model %>% select(hsol, cgsol), scale. = TRUE)
summary(pca_wealth)
merged_df_for_model$wealth_index <- pca_wealth$x[, 1]

# Village dummy variables
merged_df_for_model$village_mandena      <- ifelse(merged_df_for_model$village == "Mandena",      1, 0)
merged_df_for_model$village_sarahandrano <- ifelse(merged_df_for_model$village == "Sarahandrano", 1, 0)

# Infection status label (for model df)
merged_df_for_model <- merged_df_for_model %>%
  mutate(
    infection_status = case_when(
      bin_pos_necator == 0 & bin_pos_ancylostoma == 0 ~ "Uninfected",
      bin_pos_necator == 1 & bin_pos_ancylostoma == 0 ~ "Necator infected",
      bin_pos_necator == 0 & bin_pos_ancylostoma == 1 ~ "Ancylostoma infected",
      bin_pos_necator == 1 & bin_pos_ancylostoma == 1 ~ "Co-infected"
    )
  )

# Quadratic age term
merged_df_for_model$age2 <- merged_df_for_model$age^2
```

---

# Analysis

## Descriptive Statistics

### Demographics

```{r descriptive-stats}
# Continuous variables
continuous_summary <- merged_df_for_descriptive_stats %>%
  group_by(infection_status) %>%
  summarise(
    `Age (years)`       = mean_sd(age),
    `BMI (kg/m²)`       = mean_sd(BMI),
    `Systolic BP (mmHg)` = mean_sd(average_systolic),
    `Diastolic BP (mmHg)` = mean_sd(average_diastolic)
  ) %>%
  pivot_longer(-infection_status, names_to = "Variable", values_to = "Value")

wealth_summary <- merged_df_for_model |>
  group_by(infection_status) |>
  summarise(Wealth = mean_sd(wealth_index)) |>
  pivot_longer(-infection_status, names_to = "Variable", values_to = "Value")

sex_summary <- merged_df_for_descriptive_stats %>%
  group_by(infection_status) %>%
  summarise(
    `Female (%)` = sprintf("%d%% (n=%d)", round(mean(gender_f, na.rm = TRUE) * 100), sum(gender_f, na.rm = TRUE)),
    `Male (%)`   = sprintf("%d%% (n=%d)", round((1 - mean(gender_f, na.rm = TRUE)) * 100), sum(gender_f == 0, na.rm = TRUE))
  ) %>%
  pivot_longer(-infection_status, names_to = "Variable", values_to = "Value")

village_summary <- merged_df_for_descriptive_stats %>%
  group_by(infection_status, village) %>%
  tally() %>%
  group_by(infection_status) %>%
  mutate(percent = round(100 * n / sum(n))) %>%
  ungroup() %>%
  mutate(Variable = village, Value = sprintf("%d%% (n=%d)", percent, n)) %>%
  select(infection_status, Variable, Value)

n_row <- merged_df_for_descriptive_stats %>%
  group_by(infection_status) %>%
  summarise(Value = as.character(n()), Variable = "N") %>%
  select(Variable, everything())

table_all <- bind_rows(continuous_summary, wealth_summary, sex_summary, village_summary, n_row) %>%
  pivot_wider(names_from = infection_status, values_from = Value) %>%
  relocate(Variable)

final_table <- table_all %>%
  gt() %>%
  tab_header(title = "Descriptive statistics by infection status") %>%
  cols_label(Variable = "", Uninfected = "Uninfected",
             `Necator infected` = "Necator infected",
             `Ancylostoma infected` = "Ancylostoma infected",
             `Co-infected` = "Co-infected") %>%
  tab_spanner(label = "Infection Status",
              columns = c(Uninfected, `Necator infected`, `Ancylostoma infected`, `Co-infected`)) %>%
  sub_missing(columns = everything(), missing_text = "")

final_table |>
  tab_style(style = cell_text(weight = "bold"),
            locations = cells_body(rows = Variable == "N"))

# Gender bar chart
gender_data <- merged_df_for_model |> count(gender)
ggplot(data = gender_data, aes(x = gender, y = n, fill = gender)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis_d(begin = 0.2, end = 1) +
  ggtitle("Gender distribution (N=874)") +
  labs(x = NULL, y = "Number of participants") +
  theme(text = element_text(size = 16), axis.text = element_text(size = 16, angle = 80),
        legend.position = "none")

# Age distribution
merged_df_for_model$age_raw <- as.numeric(merged_df_for_model$age_raw)
labs_age <- c("18-19", paste(seq(20, 95, by = 5), seq(24, 99, by = 5), sep = "-"), "100+")
breaks_age <- c(18, 20, seq(25, 100, by = 5), Inf)
merged_df_for_model$AgeGroup <- cut(merged_df_for_model$age_raw, breaks = breaks_age,
                                    labels = labs_age, right = FALSE)

n_age_groups <- merged_df_for_model %>% count(AgeGroup) %>% filter(!is.na(AgeGroup))

ggplot(data = n_age_groups, aes(x = AgeGroup, y = n, fill = AgeGroup)) +
  scale_fill_viridis_d(end = .8) +
  geom_bar(stat = "identity") +
  ggtitle("Age distribution (N=874)") +
  labs(x = "Age", y = "Number of participants") +
  theme(text = element_text(size = 14), axis.text = element_text(size = 14, angle = 80),
        legend.position = "none")

cat("Mean age:", mean(merged_df_for_model$age_raw, na.rm = TRUE))
cat("SD age:",   sd(merged_df_for_model$age_raw,   na.rm = TRUE))
```

### Helminth Infection

```{r infection-prev}
n_necator     <- sum(merged_df_for_model$bin_pos_necator)
n_ancylostoma <- sum(merged_df_for_model$bin_pos_ancylostoma)
N             <- nrow(merged_df_for_model)

cat("Necator prevalence:    ", paste0(round(n_necator / N * 100, 2), "%"), "\n")
cat("Ancylostoma prevalence:", paste0(round(n_ancylostoma / N * 100, 2), "%"), "\n")
```

### BMI

```{r bmi-descriptive}
cat("Mean BMI:", mean(merged_df_for_model$BMI, na.rm = TRUE), "\n")
cat("SD BMI:",   sd(merged_df_for_model$BMI,   na.rm = TRUE), "\n")

n_underweight <- sum(merged_df_for_model$BMI < 18.5, na.rm = TRUE)
n_overweight  <- sum(merged_df_for_model$BMI > 25,   na.rm = TRUE)
cat("Underweight (<18.5):", paste0(round(n_underweight / N * 100, 2), "%"), "(n =", n_underweight, ")\n")
cat("Overweight  (>25):  ", paste0(round(n_overweight  / N * 100, 2), "%"), "(n =", n_overweight,  ")\n")

ggplot(data = merged_df_for_model, aes(x = BMI)) +
  geom_histogram(color = "white", fill = "#2c3e50", bins = 30) +
  ylim(0, 120) +
  annotate("rect",  xmin = 18.5, xmax = 24.9, ymin = 0, ymax = Inf, fill = "pink",       alpha = 0.3) +
  annotate("rect",  xmin = 25,   xmax = Inf,  ymin = 0, ymax = Inf, fill = "lightgreen", alpha = 0.3) +
  annotate("rect",  xmin = -Inf, xmax = 18.49, ymin = 0, ymax = Inf, fill = "lightblue",  alpha = 0.3) +
  annotate("text",  x = 21.7, y = Inf, label = '"Normal"', vjust = 2, size = 5, color = "darkred") +
  annotate("text",  x = 30,   y = Inf, label = '"Over"',   vjust = 2, size = 5, color = "darkgreen") +
  annotate("text",  x = 16,   y = Inf, label = '"Under"',  vjust = 2, size = 5, color = "darkblue") +
  labs(x = "BMI", y = NULL) +
  theme_minimal(base_size = 14) +
  ggtitle("Distribution of BMI (N = 874)")
```

### Blood Pressure

```{r bp-descriptive}
n_hypertensive <- merged_df_for_model |> filter(average_systolic >= 130 | average_diastolic >= 80) |> nrow()
cat("Hypertensive (systolic >=130 OR diastolic =80):", paste0(round(n_hypertensive / N * 100, 2), "%"), "\n")

ggplot(merged_df_for_model, aes(x = age, y = average_systolic, color = gender)) +
  geom_point() +
  labs(x = "Age (scaled)", y = "Average systolic BP") +
  geom_hline(yintercept = 130, color = "black") +
  ggtitle("Systolic blood pressure and age (N=874)")

ggplot(merged_df_for_model, aes(x = age, y = average_diastolic, color = gender)) +
  geom_point() +
  labs(x = "Age (scaled)", y = "Average diastolic BP") +
  geom_hline(yintercept = 80, color = "black") +
  ggtitle("Diastolic blood pressure (N=874)")
```

---

## BMI Analyses

### Model Averaging (Main)

```{r bmi-model-avg}
bmi_model_1 <- lm(
  log_BMI ~ village + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator + bin_pos_ancylostoma +
    bin_pos_necator:wealth_index + bin_pos_ancylostoma:wealth_index,
  data = merged_df_for_model, na.action = na.fail
)

dredged_bmi_model_1  <- dredge(bmi_model_1, subset = !(`I(age^2)`) | age)
averaged_bmi_model_1 <- model.avg(dredged_bmi_model_1, subset = delta < 2)

summary(averaged_bmi_model_1)
sw(averaged_bmi_model_1)

coef_bmi <- extract_coef_table(averaged_bmi_model_1, labels = var_labels)
coef_bmi <- complete_coef_table(coef_bmi, master_var_order_bmi)

p_bmi <- plot_modelavg_coef_shared(
  coef_bmi, "BMI",
  x_limits = c(-0.4, 0.6),
  importance_limits = c(0.1, 1)
)
p_bmi + theme(legend.position = "right")

# ggsave("bmi_plot_main.jpeg", path = "/Users/levkolinski/Desktop/hookworm_bmi_bloodpressure/Figures/", 
#        units="in", width=10, height=7, dpi=350, device = "jpeg", bg = "white")

# Get the scaling parameters used for log_BMI
log_bmi_values <- log(as.numeric(merged_df_for_model$BMI))
mu_log_bmi <- attr(merged_df_for_model$log_BMI, "scaled:center")  # mean of log(BMI)
sd_log_bmi <- attr(merged_df_for_model$log_BMI, "scaled:scale")   # SD of log(BMI)

# Necator coefficient on z-scaled log(BMI) — pull from your model avg object
necator_coef_z <- coef(averaged_bmi_model_1)["bin_pos_necator"]

# Convert: change in log(BMI) on original scale
delta_log_bmi <- necator_coef_z * sd_log_bmi  # e.g. -0.170 * sd

# Expected BMI for an average (z=0) person, with and without infection
bmi_uninfected <- exp(mu_log_bmi)
bmi_infected   <- exp(mu_log_bmi + delta_log_bmi)

# Absolute and % change
delta_bmi_abs <- bmi_infected - bmi_uninfected
delta_bmi_pct <- (bmi_infected / bmi_uninfected - 1) * 100

cat("Mean log(BMI):", round(mu_log_bmi, 4), "\n")
cat("SD log(BMI):", round(sd_log_bmi, 4), "\n")
cat("Necator coef (z-scale):", round(necator_coef_z, 4), "\n")
cat("Δ log(BMI) (original log scale):", round(delta_log_bmi, 4), "\n")
cat("BMI uninfected with Necator:", round(bmi_uninfected, 4), "\n")
cat("BMI infected with Necator:", round(bmi_infected, 4), "\n")
cat("Δ BMI:", round(delta_bmi_abs, 4), "kg/m²\n")
cat("% change:", round(delta_bmi_pct, 4), "%\n")
```

### Bootstrap Bonferroni-adjusted Pairwise Comparisons — BMI

```{r bmi-bootstrap}
# Create 3-level infection group variables
create_infection_group <- function(main_var, other_vars, df) {
  main_bin  <- paste0("bin_", main_var)
  others_bin <- paste0("bin_", other_vars)
  df %>%
    mutate(!!main_var := case_when(
      .data[[main_bin]] == 0 ~ "Uninfected",
      .data[[main_bin]] == 1 & rowSums(across(all_of(others_bin))) == 0 ~ "Infected only",
      .data[[main_bin]] == 1 & rowSums(across(all_of(others_bin))) > 0  ~ "Coinfected"
    ))
}

infection_vars      <- c("pos_necator", "pos_ancylostoma")
pairwise_comparisons <- combn(c("Uninfected", "Infected only", "Coinfected"), 2, simplify = FALSE)

for (var in infection_vars) {
  merged_df_for_model <- create_infection_group(var, setdiff(infection_vars, var), merged_df_for_model)
}

bootstrap_pairwise_diff_bmi <- function(df, group_var, group1, group2, outcome = "log_BMI") {
  df_sub <- df |> filter(.data[[group_var]] %in% c(group1, group2)) |> drop_na()
  df_sub[[group_var]] <- droplevels(factor(df_sub[[group_var]], levels = c(group1, group2)))

  boot_fun <- function(data, indices) {
    d <- data[indices, ]
    if (length(unique(d[[group_var]])) < 2) return(NA)
    f     <- as.formula(paste(outcome, "~", group_var, "+ village + age + I(age^2) + wealth_index + gender_f"))
    model <- tryCatch(lm(f, data = d), error = function(e) NULL)
    if (is.null(model) || any(is.na(coef(model)))) return(NA)
    preds <- d; preds[[group_var]] <- group1; mean1 <- mean(predict(model, newdata = preds), na.rm = TRUE)
    preds[[group_var]] <- group2;             mean2 <- mean(predict(model, newdata = preds), na.rm = TRUE)
    mean2 - mean1
  }

  set.seed(1234)
  boot_out <- boot(df_sub, statistic = boot_fun, R = 1000)
  boot_out$t <- boot_out$t[!is.na(boot_out$t), , drop = FALSE]
  boot_out$R <- nrow(boot_out$t)

  alpha_bonf <- 0.05 / length(pairwise_comparisons)
  ci  <- quantile(boot_out$t, c(alpha_bonf / 2, 1 - alpha_bonf / 2))
  p   <- min(1, (2 * min(mean(boot_out$t > 0), mean(boot_out$t < 0))) * length(pairwise_comparisons))

  data.frame(Infection = group_var, Group1 = group1, Group2 = group2,
             Mean_diff_g2_minus_g1 = round(mean(boot_out$t), 3),
             SE = round(sd(boot_out$t), 3), p = round(p, 3),
             CI_lower = round(ci[1], 3), CI_upper = round(ci[2], 3))
}

all_results_BMI <- list()
for (var in infection_vars)
  for (pair in pairwise_comparisons)
    all_results_BMI[[length(all_results_BMI) + 1]] <-
      bootstrap_pairwise_diff_bmi(merged_df_for_model, var, pair[1], pair[2])

comparison_table_bmi <- bind_rows(all_results_BMI)
kable(comparison_table_bmi,
      caption = "Bootstrap Bonferroni pairwise comparisons: parasite infection status ~ BMI (adjusted for age, age², sex, village, wealth)")
```

---

## Blood Pressure Analyses

### Model Averaging — Systolic BP (Continuous)

```{r systolic-model-avg}
systolic_model_1 <- lm(
  log_systolic ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator + bin_pos_necator:wealth_index +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index,
  data = merged_df_for_model, na.action = na.fail
)

dredged_systolic_model_1  <- dredge(systolic_model_1, subset = !(`I(age^2)`) | age)
averaged_systolic_model_1 <- model.avg(dredged_systolic_model_1, subset = delta < 2)

summary(averaged_systolic_model_1)
sw(averaged_systolic_model_1)


# Get the scaling parameters used for log systolic
log_systolic_values <- log(as.numeric(merged_df_for_model$average_systolic))
mu_log_systolic <- attr(merged_df_for_model$log_systolic, "scaled:center")  
sd_log_systolic <- attr(merged_df_for_model$log_systolic, "scaled:scale") 
# Necator coefficient on z-scaled log(systolic) — pull from your model avg object
necator_coef_z <- coef(averaged_systolic_model_1)["bin_pos_necator"]
ancylostoma_coef_z <- coef(averaged_systolic_model_1)["bin_pos_ancylostoma"]

# Convert: change in log(systolic) on original scale
delta_log_systolic <- necator_coef_z * sd_log_systolic  
delta_log_systolic_anc <- ancylostoma_coef_z * sd_log_systolic  

# Expected BMI for an average (z=0) person, with and without infection
systolic_uninfected <- exp(mu_log_systolic)
systolic_infected   <- exp(mu_log_systolic + delta_log_systolic)
systolic_infected_anc   <- exp(mu_log_systolic + delta_log_systolic_anc)


# Absolute and % change
delta_systolic_abs <- systolic_infected - systolic_uninfected
delta_systolic_pct <- (systolic_infected / systolic_uninfected - 1) * 100

delta_systolic_abs_anc <- systolic_infected_anc - systolic_uninfected
delta_systolic_pct_anc <- (systolic_infected_anc / systolic_uninfected - 1) * 100


cat("Mean log(systolic):", round(mu_log_systolic, 4), "\n")
cat("SD log(systolic):", round(sd_log_systolic, 4), "\n")
cat("Necator coef (z-scale):", round(necator_coef_z, 4), "\n")
cat("Δ log(systolic) (original log scale):", round(delta_log_systolic, 4), "\n")
cat("systolic uninfected with Necator:", round(systolic_uninfected, 4), "\n")
cat("systolic infected with Necator:", round(systolic_infected, 4), "\n")
cat("Δ systolic:", round(delta_systolic_abs, 4), "mmHg\n")
cat("% change:", round(delta_systolic_pct, 4), "%\n")

cat("Ancylostoma coef (z-scale):", round(ancylostoma_coef_z, 4), "\n")
cat("Δ log(systolic) (original log scale):", round(delta_log_systolic_anc, 4), "\n")
cat("systolic uninfected with Ancylostoma:", round(systolic_uninfected, 4), "\n")
cat("systolic infected with Ancylostoma:", round(systolic_infected_anc, 4), "\n")
cat("Δ systolic:", round(delta_systolic_abs_anc, 4), "mmHg\n")
cat("% change:", round(delta_systolic_pct_anc, 4), "%\n")
```

### Model Averaging — Systolic Hypertension (Binary, >130 mmHg)

```{r systolic-htn-model-avg}
systolic_htn_model <- glm(
  bin_systolic_htn ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator + bin_pos_necator:wealth_index +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index,
  data = merged_df_for_model, na.action = na.fail, family = "binomial"
)

dredged_systolic_htn_model  <- dredge(systolic_htn_model, subset = !(`I(age^2)`) | age)
averaged_systolic_htn_model <- model.avg(dredged_systolic_htn_model, subset = delta < 2)

summary(averaged_systolic_htn_model)
sw(averaged_systolic_htn_model)
```

### Model Averaging — Diastolic BP (Continuous)

```{r diastolic-model-avg}
diastolic_model_1 <- lm(
  log_diastolic ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator + bin_pos_necator:wealth_index +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index,
  data = merged_df_for_model, na.action = na.fail
)

dredged_diastolic_model_1  <- dredge(diastolic_model_1, subset = !(`I(age^2)`) | age)
averaged_diastolic_model_1 <- model.avg(dredged_diastolic_model_1, subset = delta < 2)

summary(averaged_diastolic_model_1)
sw(averaged_diastolic_model_1)


# Get the scaling parameters used for log diastolic
log_diastolic_values <- log(as.numeric(merged_df_for_model$average_diastolic))
mu_log_diastolic <- attr(merged_df_for_model$log_diastolic, "scaled:center")  
sd_log_diastolic <- attr(merged_df_for_model$log_diastolic, "scaled:scale") 
# Necator coefficient on z-scaled log(diastolic) — pull from your model avg object
necator_coef_z <- coef(averaged_diastolic_model_1)["bin_pos_necator"]
ancylostoma_coef_z <- coef(averaged_diastolic_model_1)["bin_pos_ancylostoma"]

# Convert: change in log(diastolic) on original scale
delta_log_diastolic <- necator_coef_z * sd_log_diastolic  
delta_log_diastolic_anc <- ancylostoma_coef_z * sd_log_diastolic  

# Expected BMI for an average (z=0) person, with and without infection
diastolic_uninfected <- exp(mu_log_diastolic)
diastolic_infected   <- exp(mu_log_diastolic + delta_log_diastolic)
diastolic_infected_anc   <- exp(mu_log_diastolic + delta_log_diastolic_anc)


# Absolute and % change
delta_diastolic_abs <- diastolic_infected - diastolic_uninfected
delta_diastolic_pct <- (diastolic_infected / diastolic_uninfected - 1) * 100

delta_diastolic_abs_anc <- diastolic_infected_anc - diastolic_uninfected
delta_diastolic_pct_anc <- (diastolic_infected_anc / diastolic_uninfected - 1) * 100


cat("Mean log(diastolic):", round(mu_log_diastolic, 4), "\n")
cat("SD log(diastolic):", round(sd_log_diastolic, 4), "\n")
cat("Necator coef (z-scale):", round(necator_coef_z, 4), "\n")
cat("Δ log(diastolic) (original log scale):", round(delta_log_diastolic, 4), "\n")
cat("diastolic uninfected with Necator:", round(diastolic_uninfected, 4), "\n")
cat("diastolic infected with Necator:", round(diastolic_infected, 4), "\n")
cat("Δ diastolic:", round(delta_diastolic_abs, 4), "mmHg\n")
cat("% change:", round(delta_diastolic_pct, 4), "%\n")

cat("Ancylostoma coef (z-scale):", round(ancylostoma_coef_z, 4), "\n")
cat("Δ log(diastolic) (original log scale):", round(delta_log_diastolic_anc, 4), "\n")
cat("diastolic uninfected with Ancylostoma:", round(diastolic_uninfected, 4), "\n")
cat("diastolic infected with Ancylostoma:", round(diastolic_infected_anc, 4), "\n")
cat("Δ diastolic:", round(delta_diastolic_abs_anc, 4), "mmHg\n")
cat("% change:", round(delta_diastolic_pct_anc, 4), "%\n")
```

### Model Averaging — Diastolic Hypertension (Binary, >80 mmHg)

```{r diastolic-htn-model-avg}
diastolic_htn_model <- glm(
  bin_diastolic_htn ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator + bin_pos_necator:wealth_index +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index,
  data = merged_df_for_model, na.action = na.fail, family = "binomial"
)

dredged_diastolic_htn_model  <- dredge(diastolic_htn_model, subset = !(`I(age^2)`) | age)
averaged_diastolic_htn_model <- model.avg(dredged_diastolic_htn_model, subset = delta < 2)

summary(averaged_diastolic_htn_model)
sw(averaged_diastolic_htn_model)
```

### Combined Coefficient Plot — Blood Pressure Models

```{r bp-coef-plots, fig.width=12, fig.height=8}
coef_sys     <- extract_coef_table(averaged_systolic_model_1,  labels = var_labels) |> complete_coef_table(master_var_order)
coef_sys_htn <- extract_coef_table(averaged_systolic_htn_model, labels = var_labels) |> complete_coef_table(master_var_order)
coef_dia     <- extract_coef_table(averaged_diastolic_model_1,  labels = var_labels) |> complete_coef_table(master_var_order)
coef_dia_htn <- extract_coef_table(averaged_diastolic_htn_model, labels = var_labels) |> complete_coef_table(master_var_order)

combined_bp <- bind_coef_tables(
  coef_sys, coef_dia,
  outcomes = c("Systolic", "Diastolic")
)

combined_htn <- bind_coef_tables(
  coef_sys_htn, coef_dia_htn,
  outcomes = c("Systolic", "Diastolic")
)

importance_range <- range(c(combined_htn$Importance, combined_bp$Importance), na.rm = TRUE)

x_range <- range(c(combined_htn$CI_lower_95, combined_bp$CI_upper_95), na.rm = TRUE) * 1.1

bp_colors <- c(
  "Systolic"  = "#E69F00",  
  "Diastolic" = "#0072B2"  ) 

htn_colors <- c(
  "Systolic"  = "#E69F00",  
  "Diastolic" = "#0072B2"  )

p_bp <- plot_combined_outcomes(
  combined_bp,
  plot_title        = "Continuous Blood Pressure",
  x_limits          = c(-0.5, 0.6),
  importance_limits = importance_range,
  outcome_colors    = bp_colors
)

p_htn <- plot_combined_outcomes(
  combined_htn,
  plot_title        = "Hypertension (Logit-linked)",
  x_limits          = c(-1, 1),
  importance_limits = importance_range,
  outcome_colors    = htn_colors
)
combined_plot <- (p_bp | p_htn)  +
  plot_layout(guides = "collect") & theme(legend.position = "bottom")

combined_plot + plot_annotation(tag_levels = "A")
# 
# ggsave("bp_plot_main.jpeg", path = "/Users/levkolinski/Desktop/hookworm_bmi_bloodpressure/Figures/", 
#        units="in", width=13, height=8, dpi=350, device = "jpeg", bg = "white")

```

### Bootstrap Bonferroni-adjusted Pairwise Comparisons — Blood Pressure

```{r bp-bootstrap}
bootstrap_pairwise_diff_blood_pressure <- function(df, group_var, group1, group2, outcome) {
  df_sub <- df |> filter(.data[[group_var]] %in% c(group1, group2)) |> drop_na()
  df_sub[[group_var]] <- droplevels(factor(df_sub[[group_var]], levels = c(group1, group2)))

  boot_fun <- function(data, indices) {
    d <- data[indices, ]
    if (length(unique(d[[group_var]])) < 2) return(NA)
    f     <- as.formula(paste(outcome, "~", group_var, "+ village + log_BMI + age + I(age^2) + wealth_index + gender_f"))
    model <- tryCatch(lm(f, data = d), error = function(e) NULL)
    if (is.null(model) || any(is.na(coef(model)))) return(NA)
    preds <- d; preds[[group_var]] <- group1; mean1 <- mean(predict(model, newdata = preds), na.rm = TRUE)
    preds[[group_var]] <- group2;             mean2 <- mean(predict(model, newdata = preds), na.rm = TRUE)
    mean2 - mean1
  }

  set.seed(1234)
  boot_out <- boot(df_sub, statistic = boot_fun, R = 1000)
  boot_out$t <- boot_out$t[!is.na(boot_out$t), , drop = FALSE]
  boot_out$R <- nrow(boot_out$t)

  alpha_bonf <- 0.05 / length(pairwise_comparisons)
  ci  <- quantile(boot_out$t, c(alpha_bonf / 2, 1 - alpha_bonf / 2))
  p   <- min(1, (2 * min(mean(boot_out$t > 0), mean(boot_out$t < 0))) * length(pairwise_comparisons))

  data.frame(Infection = group_var, Group1 = group1, Group2 = group2,
             Mean_diff_g2_minus_g1 = round(mean(boot_out$t), 3),
             SE = round(sd(boot_out$t), 3), p = round(p, 3),
             CI_lower = round(ci[1], 3), CI_upper = round(ci[2], 3))
}

all_results_systolic  <- list()
all_results_diastolic <- list()

for (var in infection_vars) {
  for (pair in pairwise_comparisons) {
    all_results_systolic[[length(all_results_systolic) + 1]] <-
      bootstrap_pairwise_diff_blood_pressure(merged_df_for_model, var, pair[1], pair[2], "log_systolic")
    all_results_diastolic[[length(all_results_diastolic) + 1]] <-
      bootstrap_pairwise_diff_blood_pressure(merged_df_for_model, var, pair[1], pair[2], "log_diastolic")
  }
}

comparison_table_systolic  <- bind_rows(all_results_systolic)
comparison_table_diastolic <- bind_rows(all_results_diastolic)

kable(comparison_table_systolic,  caption = "Bootstrap Bonferroni pairwise comparisons: parasite infection ~ systolic BP (adjusted for age, age², sex, BMI, village, wealth)")
kable(comparison_table_diastolic, caption = "Bootstrap Bonferroni pairwise comparisons: parasite infection ~ diastolic BP (adjusted for age, age², sex, BMI, village, wealth)")
```

---

## Structural Equation Modeling

Model fit cutoffs: CFI ≥ 0.80, RMSEA ≤ 0.08, SRMR ≤ 0.08, TLI ≥ 0.80

### Systolic BP — Continuous

```{r sem-systolic-continuous}
sem_systolic_continuous <- '
  log_BMI ~ a1*bin_pos_necator + a2*bin_pos_ancylostoma +
            a3*age + a3q*age2 + a4*gender_f + a5*wealth_index

  log_systolic ~ b*log_BMI +
                 c1p*bin_pos_necator + c2p*bin_pos_ancylostoma +
                 c3p*age + c3qp*age2 + c4p*gender_f + c5p*wealth_index +
                 c6p*village_mandena + c7p*village_sarahandrano

  ind_Necator     := a1  * b
  ind_Ancylostoma := a2  * b
  ind_age         := a3  * b
  ind_age2        := a3q * b
  ind_gender_f    := a4  * b
  ind_wealth      := a5  * b

  total_Necator     := c1p  + ind_Necator
  total_Ancylostoma := c2p  + ind_Ancylostoma
  total_age         := c3p  + ind_age
  total_age2        := c3qp + ind_age2
  total_gender_f    := c4p  + ind_gender_f
  total_wealth      := c5p  + ind_wealth
'
fit_sem_systolic_continous <- sem(sem_systolic_continuous, data = merged_df_for_model, missing = "ML")
summary(fit_sem_systolic_continous, standardized = TRUE, fit.measures = TRUE)
```

### Systolic Hypertension — Binary (>130 mmHg)

```{r sem-systolic-htn}
sem_systolic_hypertension <- '
  log_BMI ~ a1*bin_pos_necator + a2*bin_pos_ancylostoma +
            a3*age + a3q*age2 + a4*gender_f + a5*wealth_index

  bin_systolic_htn ~ b*log_BMI +
                     c1p*bin_pos_necator + c2p*bin_pos_ancylostoma +
                     c3p*age + c3qp*age2 + c4p*gender_f + c5p*wealth_index +
                     c6p*village_mandena + c7p*village_sarahandrano

  ind_Necator     := a1  * b
  ind_Ancylostoma := a2  * b
  ind_age         := a3  * b
  ind_age2        := a3q * b
  ind_gender_f    := a4  * b
  ind_wealth      := a5  * b

  total_Necator     := c1p  + ind_Necator
  total_Ancylostoma := c2p  + ind_Ancylostoma
  total_age         := c3p  + ind_age
  total_age2        := c3qp + ind_age2
  total_gender_f    := c4p  + ind_gender_f
  total_wealth      := c5p  + ind_wealth
'
fit_sem_systolic_htn <- sem(sem_systolic_hypertension, data = merged_df_for_model,
                            ordered = "bin_systolic_htn", estimator = "WLSMV")
summary(fit_sem_systolic_htn, standardized = TRUE, fit.measures = TRUE)
```

### Diastolic BP — Continuous

```{r sem-diastolic-continuous}
sem_diastolic_continuous <- '
  log_BMI ~ a1*bin_pos_necator + a2*bin_pos_ancylostoma +
            a3*age + a3q*age2 + a4*gender_f + a5*wealth_index

  log_diastolic ~ b*log_BMI +
                  c1p*bin_pos_necator + c2p*bin_pos_ancylostoma +
                  c3p*age + c3qp*age2 + c4p*gender_f + c5p*wealth_index +
                  c6p*village_mandena + c7p*village_sarahandrano

  ind_Necator     := a1  * b
  ind_Ancylostoma := a2  * b
  ind_age         := a3  * b
  ind_age2        := a3q * b
  ind_gender_f    := a4  * b
  ind_wealth      := a5  * b

  total_Necator     := c1p  + ind_Necator
  total_Ancylostoma := c2p  + ind_Ancylostoma
  total_age         := c3p  + ind_age
  total_age2        := c3qp + ind_age2
  total_gender_f    := c4p  + ind_gender_f
  total_wealth      := c5p  + ind_wealth
'
fit_sem_diastolic_continous <- sem(sem_diastolic_continuous, data = merged_df_for_model, missing = "ML")
summary(fit_sem_diastolic_continous, standardized = TRUE, fit.measures = TRUE)
```

### Diastolic Hypertension — Binary (>80 mmHg)

```{r sem-diastolic-htn}
sem_diastolic_hypertension <- '
  log_BMI ~ a1*bin_pos_necator + a2*bin_pos_ancylostoma +
            a3*age + a3q*age2 + a4*gender_f + a5*wealth_index

  bin_diastolic_htn ~ b*log_BMI +
                      c1p*bin_pos_necator + c2p*bin_pos_ancylostoma +
                      c3p*age + c3qp*age2 + c4p*gender_f + c5p*wealth_index +
                      c6p*village_mandena + c7p*village_sarahandrano

  ind_Necator     := a1  * b
  ind_Ancylostoma := a2  * b
  ind_age         := a3  * b
  ind_age2        := a3q * b
  ind_gender_f    := a4  * b
  ind_wealth      := a5  * b

  total_Necator     := c1p  + ind_Necator
  total_Ancylostoma := c2p  + ind_Ancylostoma
  total_age         := c3p  + ind_age
  total_age2        := c3qp + ind_age2
  total_gender_f    := c4p  + ind_gender_f
  total_wealth      := c5p  + ind_wealth
'
fit_sem_diastolic_htn <- sem(sem_diastolic_hypertension, data = merged_df_for_model,
                             ordered = "bin_diastolic_htn", estimator = "WLSMV")
summary(fit_sem_diastolic_htn, standardized = TRUE, fit.measures = TRUE)
```

### SEM Path Diagrams

```{r sem-path-diagrams, fig.width=6, fig.height=6}
# ── Okabe-Ito colorblind-safe palette ────────────────────────────────────────
# Color encodes SPECIES IDENTITY consistently across all panels.
# Significance is encoded by penwidth + linestyle, not hue.
#
# Species colors chosen to avoid conflict with bp_colors used in coef plot:
#   bp_colors = c(Systolic = "#E69F00", Diastolic = "#0072B2")
#
#   NEC_COL  : #CC79A7  pink-purple — N. americanus
#   ANC_COL  : #009E73  teal        — A. ceylanicum
#   BMI_COL  : #333333  near-black  — BMI mediator (structural/neutral)
#   NS_COL   : #999999  grey        — any non-significant path
#
# penwidth conventions:
#   significant (p<.05)  : penwidth = 2.5, solid
#   marginal   (p<.10)   : penwidth = 1.5, dashed
#   ns                   : penwidth = 1.0, solid, NS_COL

NEC_COL <- "#CC79A7"
ANC_COL <- "#009E73"
BMI_COL <- "#000000"
NS_COL  <- "#999999"

NEC_FILL     <- "#F5F5F0"   # neutral warm white (N. americanus)
ANC_FILL     <- "#F5F5F0"   # neutral warm white (A. ceylanicum)
BMI_FILL     <- "#EBEBEB"   # light grey (BMI node)
SYS_OUT_FILL <- "#FFFFFF"   # white fill, border colored separately
DIA_OUT_FILL <- "#FFFFFF"   # white fill, border colored separately

to_gg <- function(graph, dpi = 600, width = 5000, height = 2500) {
  svg <- export_svg(graph)
  tmp <- tempfile(fileext = ".png")
  rsvg_png(charToRaw(svg), file = tmp, width = width, height = height)
  img <- magick::image_read(tmp, density = paste0(dpi, "x", dpi))
  img <- magick::image_trim(img)
  ggplotify::as.ggplot(img)
}

# Helper: HTML table label for the outcome node.
# Font colors in the table follow the same species-identity convention:
#   significant values get their species color; ns values get NS_COL.
outcome_label <- function(title, out_fill, border_col,
                          nec_direct,  nec_indirect,
                          anc_direct,  anc_indirect,
                          nec_dir_col, nec_ind_col,
                          anc_dir_col, anc_ind_col) {
  glue::glue('<<TABLE BORDER="3" CELLBORDER="1" CELLSPACING="0" CELLPADDING="5" BGCOLOR="{out_fill}" COLOR="{border_col}">
  <TR>
    <TD COLSPAN="3" ALIGN="CENTER"><B>{title}</B></TD>
  </TR>
  <TR>
    <TD ALIGN="LEFT"><B>&#160;</B></TD>
    <TD ALIGN="CENTER"><B>Direct</B></TD>
    <TD ALIGN="CENTER"><B>Indirect</B></TD>
  </TR>
  <TR>
    <TD ALIGN="LEFT"><I>N. americanus</I></TD>
    <TD ALIGN="CENTER"><FONT COLOR="{nec_dir_col}">{nec_direct}</FONT></TD>
    <TD ALIGN="CENTER"><FONT COLOR="{nec_ind_col}">{nec_indirect}</FONT></TD>
  </TR>
  <TR>
    <TD ALIGN="LEFT"><I>A. ceylanicum</I></TD>
    <TD ALIGN="CENTER"><FONT COLOR="{anc_dir_col}">{anc_direct}</FONT></TD>
    <TD ALIGN="CENTER"><FONT COLOR="{anc_ind_col}">{anc_indirect}</FONT></TD>
  </TR>
</TABLE>>')
}

# Shared DOT template.
# Edge significance is passed as full DOT attribute strings so each edge
# can independently carry color, penwidth, and style.
make_sem_plot <- function(outcome_node_label,
                          nec_to_bmi_label,  nec_to_bmi_attrs,
                          anc_to_bmi_label,  anc_to_bmi_attrs,
                          bmi_to_out_label,  bmi_to_out_attrs,
                          nec_to_out_attrs,
                          anc_to_out_attrs,
                          outcome_node_name = "OUT") {
  grViz(glue::glue('
digraph SEM {{
  graph [layout = dot, rankdir = LR, splines = true, overlap = false,
         nodesep = 0.6, ranksep = 0.9]
  node [fontname = Helvetica, fontsize = 11]
  edge [fontname = Helvetica, fontsize = 10]

  Necator     [label=<<I>N. americanus</I>>,  shape=rectangle, style=filled, fillcolor="{NEC_FILL}"]
  Ancylostoma [label=<<I>A. ceylanicum</I>>,  shape=rectangle, style=filled, fillcolor="{ANC_FILL}"]
  BMI         [label="BMI",                   shape=rectangle, style=filled, fillcolor="{BMI_FILL}"]
  {outcome_node_name} [label={outcome_node_label}, shape=none]

  Necator     -> BMI               [label="{nec_to_bmi_label}", {nec_to_bmi_attrs}]
  Ancylostoma -> BMI               [label="{anc_to_bmi_label}", {anc_to_bmi_attrs}]
  BMI         -> {outcome_node_name} [label="{bmi_to_out_label}", {bmi_to_out_attrs}]
  Necator     -> {outcome_node_name} [{nec_to_out_attrs}]
  Ancylostoma -> {outcome_node_name} [{anc_to_out_attrs}]

  {{rank=same; Necator; Ancylostoma}}
}}'))
}

# ── Convenience attribute string builders ────────────────────────────────────
sig_attrs      <- function(col) glue::glue('color="{col}", penwidth=2.5, style=solid')
marginal_attrs <- function(col) glue::glue('color="{col}", penwidth=1.5, style=dashed')
ns_attrs       <- function()    glue::glue('color="{NS_COL}", penwidth=1.0, style=solid')

# ── Panel A: Continuous Systolic BP ──────────────────────────────────────────
# Nec->BMI: p=0.008 **  | Anc->BMI: p=0.183 ns
# BMI->BP:  p<0.001 *** | Nec->BP direct: p=0.775 ns | Anc->BP direct: p=0.029 *
# Nec indirect: p=0.019 * (sig) | Anc indirect: p=0.198 ns
bp_sys_label <- outcome_label(
  title        = "Systolic Blood Pressure",
  out_fill     = SYS_OUT_FILL,
  border_col   = "#E69F00",
  nec_direct   = "-0.018 (ns)", nec_indirect = "-0.028*",
  anc_direct   = "+0.167*",     anc_indirect = "+0.017 (ns)",
  nec_dir_col  = NS_COL,        nec_ind_col  = NEC_COL,
  anc_dir_col  = ANC_COL,       anc_ind_col  = NS_COL
)

continuous_systolic_sem_plot <- make_sem_plot(
  outcome_node_label = bp_sys_label,
  outcome_node_name  = "BP",
  nec_to_bmi_label   = "-0.170**",    nec_to_bmi_attrs = sig_attrs(NEC_COL),
  anc_to_bmi_label   = "+0.103 (ns)", anc_to_bmi_attrs = ns_attrs(),
  bmi_to_out_label   = "+0.164***",   bmi_to_out_attrs = sig_attrs(BMI_COL),
  nec_to_out_attrs   = ns_attrs(),
  anc_to_out_attrs   = sig_attrs(ANC_COL)
)

# ── Panel B: Systolic Hypertension ───────────────────────────────────────────
# Nec->BMI: p=0.007 ** | Anc->BMI: p=0.224 ns
# BMI->HTN: p=0.018 *  | Nec->HTN direct: p=0.035 * | Anc->HTN direct: p=0.105 ns
# Nec indirect: p=0.077 † (marginal) | Anc indirect: p=0.280 ns
htn_sys_label <- outcome_label(
  title        = "Systolic Hypertension",
  out_fill     = SYS_OUT_FILL,
  border_col   = "#E69F00",
  nec_direct   = "-0.201*",     nec_indirect = "-0.020\u2020",
  anc_direct   = "+0.189 (ns)", anc_indirect = "+0.012 (ns)",
  nec_dir_col  = NEC_COL,       nec_ind_col  = NEC_COL,
  anc_dir_col  = NS_COL,        anc_ind_col  = NS_COL
)

systolic_htn_sem_plot <- make_sem_plot(
  outcome_node_label = htn_sys_label,
  outcome_node_name  = "HTN",
  nec_to_bmi_label   = "-0.176**",    nec_to_bmi_attrs = sig_attrs(NEC_COL),
  anc_to_bmi_label   = "+0.104 (ns)", anc_to_bmi_attrs = ns_attrs(),
  bmi_to_out_label   = "+0.115*",     bmi_to_out_attrs = sig_attrs(BMI_COL),
  nec_to_out_attrs   = sig_attrs(NEC_COL),
  anc_to_out_attrs   = ns_attrs()
)

# ── Panel C: Continuous Diastolic BP ─────────────────────────────────────────
# Nec->BMI: p=0.008 ** | Anc->BMI: p=0.183 ns
# BMI->BP:  p<0.001 ***| Nec->BP direct: p=0.091 † | Anc->BP direct: p=0.703 ns
# Nec indirect: p=0.025 * | Anc indirect: p=0.205 ns
bp_dia_label <- outcome_label(
  title        = "Diastolic Blood Pressure",
  out_fill     = DIA_OUT_FILL,
  border_col   = "#0072B2",
  nec_direct   = "-0.110\u2020",  nec_indirect = "-0.024*",
  anc_direct   = "+0.030 (ns)",   anc_indirect = "+0.014 (ns)",
  nec_dir_col  = NEC_COL,         nec_ind_col  = NEC_COL,
  anc_dir_col  = NS_COL,          anc_ind_col  = NS_COL
)

continuous_diastolic_sem_plot <- make_sem_plot(
  outcome_node_label = bp_dia_label,
  outcome_node_name  = "BP",
  nec_to_bmi_label   = "-0.170**",    nec_to_bmi_attrs = sig_attrs(NEC_COL),
  anc_to_bmi_label   = "+0.103 (ns)", anc_to_bmi_attrs = ns_attrs(),
  bmi_to_out_label   = "+0.140***",   bmi_to_out_attrs = sig_attrs(BMI_COL),
  nec_to_out_attrs   = marginal_attrs(NEC_COL),
  anc_to_out_attrs   = ns_attrs()
)

# ── Panel D: Diastolic Hypertension ──────────────────────────────────────────
# Nec->BMI: p=0.007 ** | Anc->BMI: p=0.224 ns
# BMI->HTN: p=0.002 ** | Nec->HTN direct: p=0.043 * | Anc->HTN direct: p=0.854 ns
# Nec indirect: p=0.042 * | Anc indirect: p=0.258 ns
htn_dia_label <- outcome_label(
  title        = "Diastolic Hypertension",
  out_fill     = DIA_OUT_FILL,
  border_col   = "#0072B2",
  nec_direct   = "-0.187*",     nec_indirect = "-0.027*",
  anc_direct   = "-0.021 (ns)", anc_indirect = "+0.016 (ns)",
  nec_dir_col  = NEC_COL,       nec_ind_col  = NEC_COL,
  anc_dir_col  = NS_COL,        anc_ind_col  = NS_COL
)

diastolic_htn_sem_plot <- make_sem_plot(
  outcome_node_label = htn_dia_label,
  outcome_node_name  = "HTN",
  nec_to_bmi_label   = "-0.176**",    nec_to_bmi_attrs = sig_attrs(NEC_COL),
  anc_to_bmi_label   = "+0.104 (ns)", anc_to_bmi_attrs = ns_attrs(),
  bmi_to_out_label   = "+0.151**",    bmi_to_out_attrs = sig_attrs(BMI_COL),
  nec_to_out_attrs   = sig_attrs(NEC_COL),
  anc_to_out_attrs   = ns_attrs()
)

# ── Combine and save ──────────────────────────────────────────────────────────
sem_plot_1 <- to_gg(continuous_systolic_sem_plot) + ggtitle("Systolic Blood Pressure")
sem_plot_2 <- to_gg(systolic_htn_sem_plot)         + ggtitle("Systolic Hypertension")
sem_plot_3 <- to_gg(continuous_diastolic_sem_plot) + ggtitle("Diastolic Blood Pressure")
sem_plot_4 <- to_gg(diastolic_htn_sem_plot)         + ggtitle("Diastolic Hypertension")

combined_sem_plots <- (sem_plot_1 | sem_plot_2) / (sem_plot_3 | sem_plot_4)

combined_sem_plots +
  plot_annotation(tag_levels = "A") +
  plot_layout(heights = c(1, 1), widths = c(1, 1)) &
  theme(
    plot.margin  = margin(1, 1, 1, 1),
    panel.spacing = unit(0, "pt"),
    plot.title   = element_text(face = "bold", size = 13, hjust = 0.5)
  )


# ggsave("sem_plot_main_v2.png",
#        path   = "/Users/levkolinski/Desktop/hookworm_bmi_bloodpressure/Figures/",
#        units  = "in", width = 16, height = 8, dpi = 600,
#        device = "png", bg = "white")
```

---

# Supplementary

## Sex × Hookworm Interaction Models

### BMI — Sex Interaction

```{r bmi-sex-int}
bmi_model_with_gender_int <- lm(
  log_BMI ~ village + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator     + bin_pos_necator:wealth_index     + bin_pos_necator:gender_f +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index + bin_pos_ancylostoma:gender_f,
  data = merged_df_for_model, na.action = na.fail
)

dredged_bmi_model_with_gender_int  <- dredge(bmi_model_with_gender_int, subset = !(`I(age^2)`) | age)
averaged_bmi_model_with_gender_int <- model.avg(dredged_bmi_model_with_gender_int, subset = delta < 2)

summary(averaged_bmi_model_with_gender_int)
sw(averaged_bmi_model_with_gender_int)

coef_bmi_sex <- extract_coef_table(averaged_bmi_model_with_gender_int, labels = var_labels) |>
  complete_coef_table(master_var_order_bmi_sex)

p_bmi_sex <- plot_modelavg_coef_shared(coef_bmi_sex, "BMI",
                                       x_limits = c(-0.75, 0.75),
                                       importance_limits = c(0.2, 1))
p_bmi_sex + theme(legend.position = "right")

# ggsave("bmi_sex_interaction_plot_supp.jpeg", path = "/Users/levkolinski/Desktop/hookworm_bmi_bloodpressure/Figures/", 
#        units="in", width=10, height=7, dpi=350, device = "jpeg", bg = "white")
```

### Systolic BP — Sex Interaction

```{r systolic-sex-int}
systolic_model_1_gender_int <- lm(
  log_systolic ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator     + bin_pos_necator:wealth_index     + bin_pos_necator:gender_f +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index + bin_pos_ancylostoma:gender_f,
  data = merged_df_for_model, na.action = na.fail
)

dredged_systolic_model_1_gender_int  <- dredge(systolic_model_1_gender_int, subset = !(`I(age^2)`) | age)
averaged_systolic_model_1_gender_int <- model.avg(dredged_systolic_model_1_gender_int, subset = delta < 2)

summary(averaged_systolic_model_1_gender_int)
sw(averaged_systolic_model_1_gender_int)
```

### Systolic Hypertension — Sex Interaction

```{r systolic-htn-sex-int}
systolic_htn_model_gender_int <- glm(
  bin_systolic_htn ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator     + bin_pos_necator:wealth_index     + bin_pos_necator:gender_f +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index + bin_pos_ancylostoma:gender_f,
  data = merged_df_for_model, na.action = na.fail, family = "binomial"
)

dredged_systolic_htn_model_gender_int  <- dredge(systolic_htn_model_gender_int, subset = !(`I(age^2)`) | age)
averaged_systolic_htn_model_gender_int <- model.avg(dredged_systolic_htn_model_gender_int, subset = delta < 2)

summary(averaged_systolic_htn_model_gender_int)
sw(averaged_systolic_htn_model_gender_int)
```

### Diastolic BP — Sex Interaction

```{r diastolic-sex-int}
diastolic_model_1_gender_int <- lm(
  log_diastolic ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator     + bin_pos_necator:wealth_index     + bin_pos_necator:gender_f +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index + bin_pos_ancylostoma:gender_f,
  data = merged_df_for_model, na.action = na.fail
)

dredged_diastolic_model_1_gender_int  <- dredge(diastolic_model_1_gender_int, subset = !(`I(age^2)`) | age)
averaged_diastolic_model_1_gender_int <- model.avg(dredged_diastolic_model_1_gender_int, subset = delta < 2)

summary(averaged_diastolic_model_1_gender_int)
sw(averaged_diastolic_model_1_gender_int)
```

### Diastolic Hypertension — Sex Interaction

```{r diastolic-htn-sex-int}
diastolic_htn_model_gender_int <- glm(
  bin_diastolic_htn ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator     + bin_pos_necator:wealth_index     + bin_pos_necator:gender_f +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index + bin_pos_ancylostoma:gender_f,
  data = merged_df_for_model, na.action = na.fail, family = "binomial"
)

dredged_diastolic_htn_model_gender_int  <- dredge(diastolic_htn_model_gender_int, subset = !(`I(age^2)`) | age)
averaged_diastolic_htn_model_gender_int <- model.avg(dredged_diastolic_htn_model_gender_int, subset = delta < 2)

summary(averaged_diastolic_htn_model_gender_int)
sw(averaged_diastolic_htn_model_gender_int)
```

### Combined Coefficient Plot — Sex Interaction Models

```{r sex-int-coef-plots, fig.width=12, fig.height=8}
coef_sys_sex     <- extract_coef_table(averaged_systolic_model_1_gender_int,   labels = var_labels) |> complete_coef_table(master_var_order_sex)
coef_sys_htn_sex <- extract_coef_table(averaged_systolic_htn_model_gender_int, labels = var_labels) |> complete_coef_table(master_var_order_sex)
coef_dia_sex     <- extract_coef_table(averaged_diastolic_model_1_gender_int,  labels = var_labels) |> complete_coef_table(master_var_order_sex)
coef_dia_htn_sex <- extract_coef_table(averaged_diastolic_htn_model_gender_int,labels = var_labels) |> complete_coef_table(master_var_order_sex)


combined_bp_sex <- bind_coef_tables(
  coef_sys_sex, coef_dia_sex,
  outcomes = c("Systolic", "Diastolic")
)

combined_htn_sex <- bind_coef_tables(
  coef_sys_htn_sex, coef_dia_htn_sex,
  outcomes = c("Systolic", "Diastolic")
)

importance_range_sex <- range(c(combined_htn_sex$Importance, combined_bp_sex$Importance), na.rm = TRUE)


p_bp_sex <- plot_combined_outcomes(
  combined_bp_sex,
  plot_title        = "Continuous Blood Pressure",
  x_limits          = c(-0.5, 0.6),
  importance_limits = importance_range_sex,
  outcome_colors    = bp_colors
)

p_htn_sex <- plot_combined_outcomes(
  combined_htn_sex,
  plot_title        = "Hypertension (Logit-linked)",
  x_limits          = c(-1, 1),
  importance_limits = importance_range_sex,
  outcome_colors    = htn_colors
)

combined_plot <- (p_bp_sex | p_htn_sex)  +
  plot_layout(guides = "collect") & theme(legend.position = "bottom")

combined_plot + plot_annotation(tag_levels = "A")

# ggsave("bp_sex_interaction_plot_supp.jpeg", path = "/Users/levkolinski/Desktop/hookworm_bmi_bloodpressure/Figures/", 
#        units="in", width=13, height=8, dpi=350, device = "jpeg", bg = "white")
```

## WHO Hypertension Cutoffs

### Systolic Hypertension (>140 mmHg)

```{r systolic-htn-who}
systolic_htn_model_who <- glm(
  bin_systolic_htn_who ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator + bin_pos_necator:wealth_index +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index,
  data = merged_df_for_model, na.action = na.fail, family = "binomial"
)

dredged_systolic_htn_model_who  <- dredge(systolic_htn_model_who, subset = !(`I(age^2)`) | age)
averaged_systolic_htn_model_who <- model.avg(dredged_systolic_htn_model_who, subset = delta < 2)

summary(averaged_systolic_htn_model_who)
sw(averaged_systolic_htn_model_who)
```

### Diastolic Hypertension (>90 mmHg)

```{r diastolic-htn-who}
diastolic_htn_model_who <- glm(
  bin_diastolic_htn_who ~ village + log_BMI + age + I(age^2) + gender_f + wealth_index +
    bin_pos_necator + bin_pos_necator:wealth_index +
    bin_pos_ancylostoma + bin_pos_ancylostoma:wealth_index,
  data = merged_df_for_model, na.action = na.fail, family = "binomial"
)

dredged_diastolic_htn_model_who  <- dredge(diastolic_htn_model_who, subset = !(`I(age^2)`) | age)
averaged_diastolic_htn_model_who <- model.avg(dredged_diastolic_htn_model_who, subset = delta < 2)

summary(averaged_diastolic_htn_model_who)
sw(averaged_diastolic_htn_model_who)
```

### Combined WHO Coefficient Plot

```{r who-coef-plots, fig.width=12, fig.height=5}
coef_sys_htn_who <- extract_coef_table(averaged_systolic_htn_model_who,  labels = var_labels) |> complete_coef_table(master_var_order)
coef_dia_htn_who <- extract_coef_table(averaged_diastolic_htn_model_who, labels = var_labels) |> complete_coef_table(master_var_order)

importance_range_who <- range(c(coef_sys_htn_who$Importance, coef_dia_htn_who$Importance), na.rm = TRUE)

x_range_who <- range(c(coef_sys_htn_who$CI_lower_95, coef_sys_htn_who$CI_upper_95,
                       coef_dia_htn_who$CI_lower_95, coef_dia_htn_who$CI_upper_95), na.rm = TRUE) * 1.1

p_sys_who <- plot_modelavg_coef_shared(coef_sys_htn_who, "Systolic Hypertension (WHO)",
                                       x_limits = x_range_who, importance_limits = importance_range_who)
p_dia_who <- plot_modelavg_coef_shared(coef_dia_htn_who, "Diastolic Hypertension (WHO)",
                                       x_limits = x_range_who, importance_limits = importance_range_who)

(p_sys_who | p_dia_who) +
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
# 
# ggsave("who_bp_plot_supp.jpeg", path = "/Users/levkolinski/Desktop/hookworm_bmi_bloodpressure/Figures/", 
#        units="in",  width=14, height=8, dpi=350, device = "jpeg", bg = "white")
```
